---
title: "Appendix A - Eastern Recherche Marine Park Natural Values Report"
subtitle: "South-west Marine Parks Network"
format:
  pdf:
    output-file: "Project 4.21-Eastern-Recherche-2-Appendix A-q-Natural values.pdf"
    fig-pos: 'H'
    geometry: 
      - top=2cm
      - bottom=2.5cm
      - left=2cm
      - right=2cm
    include-in-header:
      text: |
        \usepackage{caption}
        \usepackage{float}
        \renewcommand{\thefigure}{A.\arabic{figure}}
        \captionsetup{format=plain, indention=0pt}
toc: true
execute:
  echo: false
  warning: false
  message: false
post-render: 11_move-pdf.R
---

```{r}
#| include: false
library(here)
library(ggplot2)
library(knitr)
library(terra)
library(tidyterra)
library(cowplot)
library(png)
library(grid)
library(tidytext)
library(ggtext)

# Year suffix on the fish spatial-metric PNGs (script 08 saves them with
# paste(years, collapse = "-")). Hardcoded to match the ERMP survey years used
# throughout this appendix; update if the campaign years change.
yr_suffix <- "2022-2025"

# Helper: normalise a path for use inside a raw \includegraphics{} call.
# LaTeX doesn't like backslashes in paths (an issue on Windows), so force
# forward slashes regardless of platform.
tex_path <- function(p) gsub("\\\\", "/", p)
```

# Natural Values

\captionsetup{format=plain, indention=0pt}

Understanding of natural values

## Benthic ecosystem extent

### Dominant habitat types

```{r}
#| results: "hide"
p_cat <- base::readRDS(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_predicted-habitat-categorical.rds"))
dominant_habitat_path <- here("plots/eastern-recherche/habitat/_tmp_dominant-habitat.pdf")
ggsave(dominant_habitat_path, p_cat, width = 7.5, height = 4.6, device = "pdf")
```

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.95\linewidth]{`r tex_path(dominant_habitat_path)`}
\caption{Predicted dominant habitat type from stereo-BRUV groundtruthing. Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

### Habitat distribution and probability

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.95\linewidth]{`r tex_path(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_predicted-dominant-benthos-and-combined-se.png"))`}
\caption{Predicted habitat distribution probability and uncertainty from stereo-BRUV groundtruthing. Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

### Observations

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.9\linewidth]{`r tex_path(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_scatterpie.png"))`}
\caption{Habitat classes observed in spatially balanced stereo-BRUV and drop-camera imagery visualised as spatial pie charts. Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

## Benchmarks of benthic natural values

### Sand predictions

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.95\linewidth]{`r tex_path(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_predicted-individual-habitat_sand.png"))`}
\caption{Sand: spatial plots of distribution probability and uncertainty from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth). Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

### Macroalgae predictions

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.95\linewidth]{`r tex_path(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_predicted-individual-habitat_macroalgae.png"))`}
\caption{Macroalgae: spatial plots of distribution probability and uncertainty from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth). Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

### Sessile invertebrates predictions

\begin{figure}[H]
\centering
\captionsetup{format=plain, indention=0pt}
\includegraphics[width=0.95\linewidth]{`r tex_path(here("plots/eastern-recherche/habitat/eastern-rechercheAMP_predicted-individual-habitat_sessile-invertebrates.png"))`}
\caption{Sessile invertebrates: spatial plots of distribution probability and uncertainty from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth). Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

## Benchmarks of demersal fish natural values

### Species richness

```{r}
#| results: "hide"
p_control <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_control-plot_species-richness-per-bruv.rds"))
p_bar     <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_SAC-sample.rds"))

top_row <- plot_grid(NULL, p_control, NULL, ncol = 3, rel_widths = c(0.15, 0.7, 0.15))
mid_row <- plot_grid(NULL, p_bar,     NULL, ncol = 3, rel_widths = c(0.15, 0.7, 0.15))

p_species_richness <- plot_grid(top_row, mid_row,
          nrow = 2, labels = c("a)", "b)"),
          rel_heights = c(0.6, 0.4))

species_richness_path <- here("plots/eastern-recherche/fish/_tmp_species-richness-combined.pdf")
ggsave(species_richness_path, p_species_richness, width = 7.5, height = 6.2, device = "pdf")
```

\begin{figure}[H]
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(species_richness_path)`}
\captionsetup{format=plain, indention=0pt}
\caption{Demersal fish - Species richness: (a) benchmark plots by zone and depth contour and (b) species accumulation curve by year; from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth).}
\end{figure}

\clearpage

\begin{figure}[H]
\ContinuedFloat
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(here(paste0("plots/eastern-recherche/fish/eastern-rechercheAMP_predicted-individual-fish-metric_whole-assemblage_", yr_suffix, ".png")))`}
\captionsetup{list=off, format=plain, indention=0pt}
\caption*{Figure \thefigure{} continued. (c) spatial plots of distribution probability and uncertainty; from stereo-BRUV groundtruthing.Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage

### Total abundance

```{r}
#| results: "hide"
p_control <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_control-plot_total-abundance-per-bruv.rds"))
p_bar     <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_top_maxn_bar_plot.rds"))

top_row <- plot_grid(NULL, p_control, NULL, ncol = 3, rel_widths = c(0.15, 0.7, 0.15))

p_total_abundance <- plot_grid(top_row, p_bar,
          nrow = 2, labels = c("a)", "b)"),
          rel_heights = c(0.55, 0.45))

total_abundance_path <- here("plots/eastern-recherche/fish/_tmp_total-abundance-combined.pdf")
ggsave(total_abundance_path, p_total_abundance, width = 7.5, height = 6.2, device = "pdf")
```

\begin{figure}[H]
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(total_abundance_path)`}
\captionsetup{format=plain, indention=0pt}
\caption{Demersal fish - Total abundance: (a) benchmark plots by zone and depth contour and (b) top 10 most abundant species (pooled across deployments); from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth).}
\end{figure}

\clearpage

\begin{figure}[H]
\ContinuedFloat
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(here(paste0("plots/eastern-recherche/fish/eastern-rechercheAMP_predicted-individual-fish-metric_total-abundance_", yr_suffix, ".png")))`}
\captionsetup{list=off, format=plain, indention=0pt}
\caption*{Figure \thefigure{} continued. (c) spatial plots of distribution probability and uncertainty; from stereo-BRUV groundtruthing.Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage
\newgeometry{top=2cm, bottom=2.1cm, left=2cm, right=2cm}

### Large Reef Fish Index\*

```{r}
#| results: "hide"
p_control <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_control-plot_large-reef-fish-index-biomass-g-per-bruv.rds"))
p_bar     <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_top_b20_bar_plot.rds"))

top_row <- plot_grid(NULL, p_control, NULL, ncol = 3, rel_widths = c(0.15, 0.7, 0.15))

p_lrfi <- plot_grid(top_row, p_bar,
          nrow = 2, labels = c("a)", "b)"),
          rel_heights = c(0.55, 0.45))

lrfi_path <- here("plots/eastern-recherche/fish/_tmp_lrfi-combined.pdf")
ggsave(lrfi_path, p_lrfi, width = 7.5, height = 6.2, device = "pdf")
```

\begin{figure}[H]
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(lrfi_path)`}
\captionsetup{format=plain, indention=0pt}
\caption{Demersal fish - Large Reef Fish Index*: (a) benchmark plots by zone and depth contour and (b) top 10 greatest biomass species (pooled across deployments); from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth). *Large Reef Fish Index representing the biomass of all fish greater than 20 cm (B20) has been adapted here for stereo-BRUV data by removing sharks and rays.}
\end{figure}

\clearpage

\begin{figure}[H]
\ContinuedFloat
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(here(paste0("plots/eastern-recherche/fish/eastern-rechercheAMP_predicted-individual-fish-metric_large-reef-fish-index_", yr_suffix, ".png")))`}
\captionsetup{list=off, format=plain, indention=0pt}
\caption*{Figure \thefigure{} continued. (c) spatial plots of distribution probability and uncertainty; from stereo-BRUV groundtruthing.Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}

\clearpage
\restoregeometry

### Reef fish thermal index

```{r}
#| results: "hide"
p_control <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_control-plot_community-thermal-index-c.rds"))
p_bar     <- base::readRDS(here("plots/eastern-recherche/fish/eastern-rechercheAMP_top_maxn_cti_bar_plot.rds"))

top_row <- plot_grid(NULL, p_control, NULL, ncol = 3, rel_widths = c(0.15, 0.7, 0.15))

p_thermal <- plot_grid(top_row, p_bar,
          nrow = 2, labels = c("a)", "b)"),
          rel_heights = c(0.55, 0.45))

thermal_path <- here("plots/eastern-recherche/fish/_tmp_thermal-combined.pdf")
ggsave(thermal_path, p_thermal, width = 9.5, height = 8, device = "pdf")
```

\begin{figure}[H]
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(thermal_path)`}
\captionsetup{format=plain, indention=0pt}
\caption{Demersal fish - Reef Fish Thermal Index: (a) benchmark plots by zone and depth contour, with monthly sea surface temperature (black line, grey band = SD) overlaid, and (b) species thermal niche of top 10 most abundant species (pooled across deployments); from stereo-BRUV groundtruthing. ERMP = Eastern Recherche Marine Park (Commonwealth).}
\end{figure}

\clearpage

\begin{figure}[H]
\ContinuedFloat
\centering
\includegraphics[width=0.95\linewidth]{`r tex_path(here(paste0("plots/eastern-recherche/fish/eastern-rechercheAMP_predicted-individual-fish-metric_cti_", yr_suffix, ".png")))`}
\captionsetup{list=off, format=plain, indention=0pt}
\caption*{Figure \thefigure{} continued. (c) spatial plots of distribution probability and uncertainty; from stereo-BRUV groundtruthing.Commonwealth marine park boundaries are shown. The red line delimits state and commonwealth waters. Bathymetric contour at 30 m is shown.}
\end{figure}
